---
title: "Data formatting EHT"
output:
  word_document: default
  html_document: default
date: "2024-11-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( results='hide')

rm(list=ls())
library(dplyr)
library(ggplot2)
library(readxl)
library(stringr)
library(tidyr)
library(gt)
library(haven)

mainDir="."
plotDir=file.path(mainDir, "plots")
dataDir=file.path(mainDir, "data")
outputsDir=file.path(mainDir, "csv_outputs")

scriptDir=file.path(mainDir,"EHT_fit")

```

# Data processing
## Kibondo et al. 2022

Import dataset and select main variables
```{r,  results='hide' }
data_kibondo_0<-read_excel(file.path(dataDir,"G2expermentalhutdata_21dec2022_kibondo2022Hut.xlsx"), sheet=1)
data_kibondo=data_kibondo_0 %>%
  filter(specie=="arabiensis", lntype!="Control", timeperiod %in% c(24, 72)) %>%
  rename(UA=(unfedalive), FA=(fedalive), UD=(unfeddead), FD=(feddead), insecticide_name=lntype) %>%
  mutate(treatment=ifelse(nettype %in% c("Unw Inter", "Washed Inter"), 0,
                                  ifelse( nettype %in% c("Unw InterG2", "Washed IntrG2"), 1, NA)),
         total=UA+UD+FA+FD, fed=FA+FD, dead=UD+FD,
         )%>%
  select(date, studyday, hutno, timeperiod, specie, volunteer,wash_status, insecticide_name, treatment, nettype, UA, UD, FA, FD, dead, fed, total)
```

Save file.
```{r,  results='hide'  }

write.csv(data_kibondo %>% filter(timeperiod==72), file = file.path(outputsDir, "kibondo_reformat_72.csv"), row.names = F)
write.csv(data_kibondo  %>% filter(timeperiod==24), file = file.path(outputsDir, "kibondo_reformat_24.csv"), row.names = F)

```


## BIT103
Import dataset, rename and select main variables  (we obtain the netIDs and the hut numbers corresponding to Ifakara huts from a previous file)

```{r  warning=FALSE ,  results='hide'}
data_bit103_old<-read_excel(file.path(dataDir,"BIT103_Ifakara_Huts_data.xlsx"), sheet=1)
data_bit103_0<-read_excel(file.path(dataDir,"BIT103_All_Data_AAA_II.xlsx"), sheet="EH_ALL_DATA")

netcodes_103=data_bit103_old%>% select(netcode, arm, Nettype, wash, ITN)%>%
  rename(test_item_number=netcode)%>% unique()

data_bit103=data_bit103_0%>%
  ungroup()%>%
  select(-study_director, - project_name, -entered_by, -trap_id, -trap_name, -total_number_of_huts, -mosquitoes_strain_id, -serial_number)%>%
  group_by(day, test_item_number, date_test,hut_number, sleeper, mosquitoes_strain_name )%>%
  summarise_all(list(sum))%>%
  ungroup()%>%
  merge(netcodes_103)%>% 
  mutate(treatment=ifelse(ITN=="MagNet_ITN", 0,
                          ifelse(ITN=="Olyset_Plus", 1,
                                 ifelse( ITN=="Interceptor_G2", 2, NA))), 
         insecticide_name=ITN, wash_status=as.character(wash))

names(data_bit103)=gsub("amekula_", "F", gsub("hajala_", "U",
                                              gsub("amekufa", "D",
                                                   gsub("wazima", "A", names(data_bit103)))))

data_bit103_ifakara=data_bit103%>%
  filter(hut_number%in% unique(data_bit103_old$hut_number))


```

Separate file per time period

```{r }
data_bit103_ifakara_72=data_bit103_ifakara %>%
  filter(mosquitoes_strain_name=="Anopheles gambiae s.l") %>%
  rename(UD_12=UD, UA_12=UA, FA_12=FA, FD_12=FD)%>%
  mutate(UA=UA_72,
         FA=FA_72,
         UD= UD_72,
         FD=FD_72,
         total=UA+UD+FA+FD, fed=FA+FD, dead=FD+UD
  )%>%
  select(date_test, day, hut_number, mosquitoes_strain_name, sleeper,wash_status, insecticide_name, treatment, Nettype, UA, UD, FA, FD, dead, fed, total)

data_bit103_ifakara_24=data_bit103_ifakara %>%
  filter(mosquitoes_strain_name=="Anopheles gambiae s.l") %>%
  rename(UD_12=UD, UA_12=UA, FA_12=FA, FD_12=FD)%>%
  mutate(UA=UA_24,
         FA=FA_24,
         UD= UD_24,
         FD=FD_24,
         total=UA+UD+FA+FD, fed=FA+FD, dead=FD+UD
  )%>%
  select(date_test, day, hut_number, mosquitoes_strain_name, sleeper,wash_status, insecticide_name, treatment, Nettype, UA, UD, FA, FD, dead, fed, total)

```


Save files

```{r ,  results='hide' , warning=FALSE}

write.csv(data_bit103_ifakara_72, file = file.path(outputsDir, "bit103_reformat_new_ifakara_72.csv"), row.names = F)
write.csv(data_bit103_ifakara_24, file = file.path(outputsDir, "bit103_reformat_new_ifakara_24.csv"), row.names = F)


```

## BIT055

Import dataset, rename and select main variables  (we obtain the netIDs from a previous file)

```{r ,  results='hide' , warning=FALSE }
data_bit055_old<-read.csv(file.path(dataDir,"BIT055_data.csv"))
data_bit055_0<-read_excel(file.path(dataDir,"BIT055_GF_ Experimental_hut_LOCK.xlsx"), sheet=1)

bit055_netcodes=data_bit055_old%>% select(netcode, netid,washed, netBrand)%>% unique()

data_bit055=data_bit055_0%>% 
  rename(netcode="Net/Treatment no.", hutno="Namba ya kibanda")%>%
  select(- "Form row", -Trap_ID, -"Project Code")%>%
  group_by(Serial, Date, hutno,netcode, Aliyelala , species)%>%
  summarise_all(list(sum))%>%
  ungroup()%>% 
  left_join(bit055_netcodes)%>%
  filter(species=="arabiensis",
         netid %in% c("UOlysetPlus" ,"WOlysetPlus", "UOlyset","WOlyset" ))%>%
  mutate(treatment=ifelse( netid  %in% c("UOlyset" ,"WOlyset"), 0,
                                  ifelse( netid  %in% c("UOlysetPlus" ,"WOlysetPlus"), 1, NA)),
         insecticide_name=gsub("ontrol", "Control",substring(netid, 2)), 
         wash_status=as.character(washed)
         )

names(data_bit055)=gsub("amekula", "F", gsub("hajala", "U",
                                              gsub("amekufa", "D",
                                                   gsub("wazima", "A", gsub(" ", "", names(data_bit055))))))


data_bit055_24=data_bit055 %>%
  select(-UD, -UA, -FD, -FA)%>%
  rename(UD=UD24, UA=UA24, FD=FD24, FA=FA24)%>%
  mutate(total=UA+UD+FA+FD, fed=FA+FD, dead=UD+FD)

```


Save files

```{r }
write.csv(data_bit055_24, file = file.path(outputsDir, "bit055_reformat_24.csv"), row.names = F)


```

## BIT059

Import dataset, rename and select main variables

```{r ,  results='hide' , warning=FALSE }
data_bit059_0<-read_excel(file.path(dataDir,"Experimental hut data_cleaned_59_80_full.xls"), sheet="BIT059 Cleaned")

data_bit059=data_bit059_0%>% 
  filter(meannetid %in% c("OlysetPlus", "PermaNet2.0"))%>%
  mutate(treatment=ifelse( meannetid  == "PermaNet2.0" , 0,
                                  ifelse( meannetid =="OlysetPlus", 1, NA)),
         insecticide_name=meannetid, 
         wash_status=as.character(condition)
         )%>%
  rename(UD=unfeddead24, UA=unfedalive24, FD=feddead24, FA=fedalive24)%>%
  mutate(total=UA+UD+FA+FD, fed=FA+FD, dead=UD+FD)%>%
  select(day, hutno, specie, netcode, volunteer, UA, UD, FD, FA, fed, total, dead, arm, netid, wash_status, insecticide_name, treatment)

```


Save files

```{r }
write.csv(data_bit059, file = file.path(outputsDir, "bit059_reformat_24.csv"), row.names = F)

```

## BIT080

Import dataset, rename and select main variables

```{r ,  results='hide' , warning=FALSE }
data_bit080_0<-read_excel(file.path(dataDir,"Experimental hut data_cleaned_59_80_full.xls"), sheet="BIT080 Cleaned")

data_bit080=data_bit080_0%>% 
  filter(meannetid %in% c("InterceptorG2", "MiraNet"))%>%
  mutate(treatment=ifelse( meannetid  == "MiraNet" , 0,
                                  ifelse( meannetid =="InterceptorG2", 1, NA)),
         insecticide_name=meannetid, 
         wash_status=as.character(condition)
         )

data_bit080_24=data_bit080 %>%
  rename(UD=unfeddead24, UA=unfedalive24, FD=feddead24, FA=fedalive24)%>%
  mutate(total=UA+UD+FA+FD, fed=FA+FD, dead=UD+FD)%>%
  select(day, hutno, specie, netcode, volunteer, UA, UD, FD, FA, fed, total, dead, arm, netid, wash_status, insecticide_name, treatment)

data_bit080_72=data_bit080 %>%
  rename(UD=unfeddead72, UA=unfedalive72, FD=feddead72, FA=fedalive72)%>%
  mutate(total=UA+UD+FA+FD, fed=FA+FD, dead=UD+FD)%>%
  select(day, hutno, specie, netcode, volunteer, UA, UD, FD, FA, fed, total, dead, arm, netid, wash_status, insecticide_name, treatment)

```


Save files

```{r }
write.csv(data_bit080_24, file = file.path(outputsDir, "bit080_reformat_24.csv"), row.names = F)
write.csv(data_bit080_72, file = file.path(outputsDir, "bit080_reformat_72.csv"), row.names = F)


```


# Summary tables

## Total numbers

```{r,  results='hide', message=FALSE }
# function to aggregate data
summarise_EHTdata_total=function(df, EHT, holdingtime){
  p= df %>%
    mutate(total=UA+UD+FA+FD)%>%
    group_by(insecticide_name, wash_status) %>%
    summarise(Total=sum(total, na.rm=TRUE),
              UA=sum(UA, na.rm=TRUE), UD=sum(UD, na.rm=TRUE), FA=sum(FA, na.rm=TRUE),FD=sum(FD, na.rm=TRUE)
    )%>%
    mutate(EHT=EHT, holdingtime=paste0(holdingtime, "h"))
  
  return(p)
}

# apply to all datasets
all_data_sum_species_total=rbind(summarise_EHTdata_total( data_kibondo%>% filter(timeperiod==24), EHT="Kibondo\net al. 2022", holdingtime=72),
                                 summarise_EHTdata_total( data_kibondo %>% filter(timeperiod==24), EHT="Kibondo\net al. 2022", holdingtime=24),
                                 summarise_EHTdata_total( data_bit103_ifakara_24, EHT="BIT103", holdingtime=24),
                                 summarise_EHTdata_total( data_bit103_ifakara_72, EHT="BIT103", holdingtime=72),
                                 summarise_EHTdata_total( data_bit055_24, EHT="BIT055", holdingtime=24),
                                 summarise_EHTdata_total( data_bit080_72, EHT="BIT080", holdingtime=72),
                                 summarise_EHTdata_total( data_bit059, EHT="BIT059", holdingtime=24),
                                 summarise_EHTdata_total( data_bit080_24, EHT="BIT080", holdingtime=24)
                                 
)%>%
  mutate(insecticide_name=ifelse(insecticide_name %in% c("IG2", "Interceptor_G2","Interceptor®G2", "Interceptor G2"), "Interceptor G2",
                                 ifelse(insecticide_name %in% c("Olyset_Plus","OlysetPlus"), "Olyset Plus", insecticide_name)),
         wash_status=ifelse(wash_status %in% c(0, "Unwashed"), "Unwashed", "20x"))


```

Supplementary table 1: Total numbers of mosquitoes for the three experimental hut trials considered. Each quantity refers to total value summing over all nights in each experiment for each arm. 
UA: Unfed alive ; UD: Unfed dead ; FA: Fed alive ; FD: Fed dead.

```{r, echo=T, results='asis'}
total_table=all_data_sum_species_total %>%
  ungroup()%>%
  arrange(EHT, holdingtime,insecticide_name, wash_status)%>%
  select(EHT,holdingtime, insecticide_name, wash_status,  Total, UA, UD, FA, FD) %>%
  rename("Net type"=insecticide_name, "Washed status"=wash_status, "Holding time"=holdingtime)%>%
  group_by(EHT)%>%
  gt() 

#total_table%>%  gt::gtsave(filename = file.path(plotDir, "my_table_total_wash.docx"))
total_table



```

only maximal holding time
```{r, echo=T, results='asis'}
total_table=all_data_sum_species_total %>%
  filter(holdingtime ==ifelse(EHT %in% c("BIT055","BIT059" ),"24h", "72h" ))%>%
  ungroup()%>%
  arrange(EHT,insecticide_name, wash_status)%>%
  select(EHT,insecticide_name, wash_status,  Total, UA, UD, FA, FD) %>%
  rename("Net type"=insecticide_name, "Washed status"=wash_status)%>%
  group_by(EHT)%>%
  gt() 

#total_table%>%  gt::gtsave(filename = file.path(plotDir, "my_table_total_wash.docx"))
total_table



```


## Average per night
```{r, results='hide', message=FALSE }
# function to aggregate data
summarise_EHTdata_perNight=function(df, EHT, holdingtime){
  p= df %>%
    mutate(fed= (FA+FD)/total,
           dead=(FD+UD)/total,
           total=UA+UD+FA+FD,
           propUD=UD/(total))%>%
    group_by(insecticide_name, wash_status) %>%
    summarise(fed_mean=mean(fed, na.rm=TRUE), dead_mean=mean(dead, na.rm=TRUE), total_mean=mean(total, na.rm=TRUE),
              fed_sd=sd(fed, na.rm=TRUE), dead_sd=sd(dead, na.rm=TRUE), total_sd=sd(total, na.rm=TRUE),
              fed_sd=sd(fed, na.rm=TRUE), dead_sd=sd(dead, na.rm=TRUE), total_sd=sd(total, na.rm=TRUE),
              UA_mean=mean(UA, na.rm=TRUE), UD_mean=mean(UD, na.rm=TRUE), FA_mean=mean(FA, na.rm=TRUE),FD_mean=mean(FD, na.rm=TRUE),F_mean=mean(FD+FA, na.rm=TRUE),
              UA_sd=sd(UA, na.rm=TRUE), UD_sd=sd(UD, na.rm=TRUE), FA_sd=sd(FA, na.rm=TRUE), FD_sd=sd(FD, na.rm=TRUE), F_sd=sd(FD+FA, na.rm=TRUE),
              propUD_mean=mean(propUD, na.rm=TRUE),
              propUD_sd=sd(propUD, na.rm=TRUE),
    )%>%
    tidyr::pivot_longer(cols = c(fed_mean, dead_mean, total_mean,
                                 fed_sd, dead_sd, total_sd,
                                 UA_mean, UD_mean, F_mean, FA_mean, FD_mean,
                                 UA_sd, UD_sd, F_sd, FA_sd, FD_sd,
                                 propUD_mean,propUD_sd ), names_to = "quantity"
    ) %>%
    tidyr::separate(col=quantity, into = c("name","stat" ), sep = "_")%>%
    pivot_wider(id_cols = c("insecticide_name", "wash_status", "name"),names_from= "stat", values_from="value")%>%
    mutate(name=factor(name, levels=c("fed", "dead", "total","UA", "UD", "FA", "FD", "F", "propUD"),
                       labels=c("Fed", "Dead", "Total", "UA", "UD", "FA", "FD", "F", "propUD")),
           EHT=EHT, holdingtime=paste0(holdingtime, "h"))
  
  return(p)
}

# apply to all datasets
all_data_sum_species_perNight=rbind(summarise_EHTdata_perNight( data_kibondo%>% filter(timeperiod==24), EHT="Kibondo\net al. 2022", holdingtime=72),
                                 summarise_EHTdata_perNight( data_kibondo %>% filter(timeperiod==24), EHT="Kibondo\net al. 2022", holdingtime=24),
                                 summarise_EHTdata_perNight( data_bit103_ifakara_24, EHT="BIT103", holdingtime=24),
                                 summarise_EHTdata_perNight( data_bit103_ifakara_72, EHT="BIT103", holdingtime=72),
                                 summarise_EHTdata_perNight( data_bit055_24, EHT="BIT055", holdingtime=24),
                                 summarise_EHTdata_perNight( data_bit080_72, EHT="BIT080", holdingtime=72),
                                 summarise_EHTdata_perNight( data_bit059, EHT="BIT059", holdingtime=24),
                                 summarise_EHTdata_perNight( data_bit080_24, EHT="BIT080", holdingtime=24)
                                 
)%>%
  mutate(insecticide_name=ifelse(insecticide_name %in% c("IG2", "Interceptor_G2","Interceptor®G2", "Interceptor G2"), "Interceptor G2",
                                 ifelse(insecticide_name %in% c("Olyset_Plus","OlysetPlus"), "Olyset Plus", insecticide_name)),
         wash_status=ifelse(wash_status %in% c(0, "Unwashed"), "Unwashed","Washed 20x"),
         lower_b=pmax(mean-2*sd, 0), upper_b=ifelse(name %in% c("Fed", "Dead"), pmin(mean+2*sd,1), mean+2*sd))


```

Supplementary table 2: Summary statistics for the three experimental hut trials. Each quantity refers to average value over all nights in the experiment,  “Fed” and “Dead” correspond to respectively to (FA+FD)/Total and (UD+FD)/Total. Uncertainty intervals correspond to the mean value ± 2 standard deviations (capped to the [0-1] intervals for the proportions of fed and dead). UA: Unfed alive ; UD: Unfed dead ; FA: Fed alive ; FD: Fed dead.

```{r, echo=T, results='asis'}

perNight_table=all_data_sum_species_perNight %>%
  filter(holdingtime ==ifelse(EHT %in% c("BIT055","BIT059" ),"24h", "72h" ))%>%
  filter(! name %in% c("propUD", "F"))%>%
  mutate(mean=ifelse(name %in% c("Fed", "Dead"), round(mean, digits = 2), round(mean, digits = 0)),
         lower_b=ifelse(name %in% c("Fed", "Dead"), round(lower_b, digits = 2), round(lower_b, digits = 0)),
         upper_b=ifelse(name %in% c("Fed", "Dead"), round(upper_b, digits = 2), round(upper_b, digits = 0)))%>%
  mutate(value=paste0(mean, " (", lower_b, "-", upper_b, ")"))%>%
  select(EHT, insecticide_name, wash_status, name, value) %>%
  pivot_wider(id_cols = c(EHT, insecticide_name, wash_status), names_from = name, values_from = c(value))%>%
  arrange(EHT, insecticide_name, wash_status)%>%
  rename("Net type"=insecticide_name, "Wash status"=wash_status)%>%
  group_by(EHT)%>%
  gt() 

#perNight_table%>%  gt::gtsave(filename = file.path(plotDir, "my_table_perNight_wash.docx"))
perNight_table


```

